---
title: "causal_inference"
author: "Niander Assis"
date:
output: 
  html_document:
    fig_width: 9
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, vspaceecho = "1em", vspaceout = "1em")
knitr::opts_knit$set(root.dir = rprojroot::find_root(rprojroot::is_rstudio_project))

hook_source_def = knitr::knit_hooks$get('source')
knitr::knit_hooks$set(source = function(x, options) {
  if (!is.null(options$vspaceecho)) {
    begin <- paste0("\\vspace{", options$vspaceecho, "}")
    stringr::str_c(begin, hook_source_def(x, options))
  } else {
    hook_source_def(x, options)
  }
})

hook_output_def = knitr::knit_hooks$get('output')
knitr::knit_hooks$set(output = function(x, options) {
  if (!is.null(options$vspaceout)) {
    end <- paste0("\\vspace{", options$vspaceout, "}")
    stringr::str_c(hook_output_def(x, options), end)
  } else {
    hook_output_def(x, options)
  }
})

```

```{r source, echo = FALSE, include = FALSE}
source("src/causal_inference.R")
source("src/results_functions.R")
# library(gridExtra)
# library(gtable)
# library(grid)
library(cowplot)

theme_set(theme_cowplot(font_size = 12) +
            theme(legend.position = "bottom", legend.justification = "center"))
#theme_set(theme_gray() + 
#            theme(legend.position = "bottom", legend.justification = "center"))

JUST_HOME = TRUE
SAVE_OUTPUT = TRUE

methods =  c("nobal", "maha", "propensity.nocalip")#, "propensity")
year <- c("2017")
JoinAllMatchesAndDeltaWithData(year, methods, data = res.timeout.effect.data)

methods =  c("nobal", "maha", "propensity.nocalip")
all.mat <- env_get_list(global_env(), nms = str_c("mat", methods, sep = ".")) %>%
  modify(~ drop_na(., match.id)) %>%
  set_names(methods) %>%
  bind_rows(.id = "method") %>%
  mutate(method = fct_relevel(method, !!!methods))

PrintTableOnes <- function(df, xvars = .(slope.before, quarter, seconds, margin), print.it = F) {
  tabones <- list()
  i <- 1
  for(dta in config$deltas) {
    if (print.it) print(str_glue("===========================\ndelta: {dta}"))
    data <- df %>% filter(delta == dta)
    ddply(data, .(match.poss), function(d) {
      if(JUST_HOME) {
        if(d$match.poss[1] != "home") return()
      }
      tab.one <- CreateTableOne(vars = as.character(xvars), strata = c("treatment"), data = d, test = F)
      if (print.it) print(str_glue("poss:  {d$match.poss[1]}"))
      l <- print(tab.one, noSpaces = T, smd = T, printToggle = print.it)
      #tabones <<- list_merge(tabones, !!str_c(dta, d$match.poss[1]) := as.matrix(l))
      tabones[[i]] <<- l
      i <<- i + 1
      return(NULL)
    })
  }
  if (print.it) print(str_glue("==========================="))
  return(invisible(tabones))
}

PrintTableOnesUnify <- function(df, xvars = .(slope.before, quarter, seconds, margin), print.it = F) {
  df %<>%
    mutate_at(vars(slope.before, slope.after, infl.score), funs(if_else(match.poss == "away", -1 * ., .)))
  tabones <- list()
  i <- 1
  for(dta in config$deltas) {
    if (print.it) print(str_glue("===========================\ndelta: {dta}"))
    d <- df %>% filter(delta == dta)
    tab.one <- CreateTableOne(vars = as.character(xvars), strata = c("treatment"), data = d, test = F)
    l <- print(tab.one, noSpaces = T, smd = T, printToggle = print.it)
    #tabones <<- list_merge(tabones, !!str_c(dta, d$match.poss[1]) := as.matrix(l))
    tabones[[i]] <- l
    i <- i + 1
  }
  if (print.it) print(str_glue("==========================="))
  return(invisible(tabones))
}

library(brew)

BrewTableOne <- function(tab.ones, suffix.name) {
  deltas <- config$deltas
  brew.tab.ones <- "\\begin{tabular}{ccccccc} \\toprule
  <% for(i in 1:length(tab.ones)) { -%>
  <% tab <- tab.ones[[i]] -%>
  $\\lambda$ = <%= deltas[[i]] %> & control & timeout & SMD \\\\ \\midrule
  n & <%= tab[1,1] %> & <%= tab[1,2] %> & ---\\\\
  \\stmcB (mean (sd)) & <%= tab[2,1] %> & <%= tab[2,2] %> & <%= tab[2,3] %> \\\\
  quarter (mean (sd)) & <%= tab[3,1] %> & <%= tab[3,2] %> & <%= tab[3,3] %> \\\\
  seconds (mean (sd)) & <%= tab[4,1] %> & <%= tab[4,2] %> & <%= tab[4,3] %> \\\\
  $P_i$ (mean (sd)) & <%= tab[5,1] %> & <%= tab[5,2] %> & <%= tab[5,3] %> \\\\ <% if(i < length(tab.ones)) { -%> 
  \\midrule
  <% } %>
  <% } -%>
  \\bottomrule
  \\end{tabular}%"
  if(SAVE_OUTPUT) brew(text = brew.tab.ones, output = path("reports", str_c("latex.table", suffix.name, "txt", sep = ".")))
}


SaveGraph <- function(fname, plot = last_plot(), device = "pdf", width = 7.28, height = 5) {
  if(SAVE_OUTPUT) ggsave(path("graphs", fname),
                         plot = plot,
                         device = device, width = width, height = height)
}

```

# Prior Matching
```{r}
tabs <- PrintTableOnes(mat.nobal)
BrewTableOne(tabs, str_c("nomat", year, sep = "."))
tabs <- PrintTableOnesUnify(mat.nobal)
BrewTableOne(tabs, str_c("nomat", year, "unify", sep = "."))
```

# After no balance matching
```{r}
tabs <- PrintTableOnes(mat.nobal %>% drop_na(match.id))
BrewTableOne(tabs, str_c("nobal", year, sep = "."))
tabs <- PrintTableOnesUnify(mat.nobal %>% drop_na(match.id))
BrewTableOne(tabs, str_c("nobal", year, "unify", sep = "."))
```

# After Matching maha
```{r}
tabs <- PrintTableOnes(mat.maha %>% drop_na(match.id))
BrewTableOne(tabs, str_c("maha", year, sep = "."))
tabs <- PrintTableOnesUnify(mat.maha %>% drop_na(match.id))
BrewTableOne(tabs, str_c("maha", year, "unify", sep = "."))
```

# After Matchin Maha with replacement
```{r}
#PrintTableOnes(mat.maha %>% drop_na(match.id))
```

# After Matching propensity no caliper
```{r}
tabs <- PrintTableOnes(mat.propensity.nocalip %>% drop_na(match.id))
BrewTableOne(tabs, str_c("propensity.nocalip", year, sep = "."))
tabs <- PrintTableOnesUnify(mat.propensity.nocalip %>% drop_na(match.id))
BrewTableOne(tabs, str_c("propensity.nocalip", year, "unify", sep = "."))
```

# After Matching propensity with caliper
```{r}
tabs <- PrintTableOnes(mat.propensity %>% drop_na(match.id))
BrewTableOne(tabs, str_c("propensity", year, sep = "."))
tabs <- PrintTableOnesUnify(mat.propensity %>% drop_na(match.id))
BrewTableOne(tabs, str_c("propensity", year, "unify", sep = "."))
```

# All tables

```{r}
BrewBigTableOne <- function(tab.ones, suffix.name) {
  qtd.methods <- length(methods) + 1 #plus 1 for unmatch
  qtd.deltas <- length(config$deltas)
  tab.deltas <- rep(config$deltas, each = qtd.methods)
  methods <- c("unmatch", methods)
  tab.methods <- methods %>%
    as_list() %>%
    set_names(methods) %>%
    list_modify(unmatch = "Before Matching", nobal = "No-balance", 
                maha = "Mahalanobis", propensity.nocalip = "Propensity",
                propensity = "Propensity with caliper") %>%
    squash_chr() %>%
    extract(methods) %>%
    rep(length(config$deltas))
  
  if(SAVE_OUTPUT) brew(file=str_c(rprojroot::find_root(rprojroot::is_rstudio_project), "/lib/", "tab.ones.brew"), 
                       output = str_c("latex.table", suffix.name, "txt", sep = "."))
}

all.tab.ones <- all.mat %>%
  mutate_at(vars(method), as.character) %>%
  bind_rows(mat.nobal %>% mutate(method = "unmatch")) %>%
  mutate(method = fct_relevel(method, c("unmatch", methods))) %>%
  dlply(.(method), function(df) {
    PrintTableOnesUnify(df, print.it = F)
  }) %>%
  transpose() %>%
  flatten()

BrewBigTableOne(all.tab.ones, str_c("all.methods", year, sep = "."))

```

# SMD comparisson

```{r, results = "hold"}
xvars = exprs(quarter, seconds, margin)
plot.data <- bind_rows(all.mat,
                       mat.nobal %>% mutate(method = "unmatch")) %>%
  group_by(method, delta) %>%
  do(tableone = as.data.frame(t(ExtractSmd(CreateTableOne(vars = as.character(xvars), strata = "A", data = ., test = F))))) %>%
  unnest(tableone)

plot.data %<>%
  gather(key = "var", value = "smd", !!!xvars)

plt <- plot.data %>% 
  #filter(!JUST_HOME | match.poss == "home") %>%
  ggplot(aes(x = method)) +
  geom_point(aes(y=smd, color = var)) +
  geom_line(aes(y=smd, color = var, group = var)) +
  scale_x_discrete(limits = c("unmatch", methods)) +
  geom_hline(yintercept = 0.1, linetype = 2, size = 0.2)

if (JUST_HOME) {
  plt + facet_grid(delta ~ .)
} else {
  plt + facet_grid(delta ~ match.poss)
}

#ggsave(path(projroot, "graphs", "smd-lines.pdf"), device = "pdf", width = 7.28, height = 4)

```

# Seconds and quarter distribution plots for $\lambda = 2$

```{r, results = "hold", cache = F}

PlotAux <- function(df) {
  plot.data <- df %>%
    filter(delta == 4) %>%
    drop_na(match.id)
  
  plt1 <- ggplot(plot.data, aes(seconds, fill = treatment, color = treatment)) +
    #geom_histogram(binwidth = 30, position = "identity", alpha = 0.2)
    geom_histogram(aes(y = stat(count / sum(count))), 
                   binwidth = 10, position = "identity", alpha = 0.2) +
    #geom_freqpoly(binwidth = 20) + 
    #geom_bar(alpha = 0.2, position = "identity") + 
    #stat_count(geom = "step", position = "identity") +
    #geom_density(alpha = 0.2, adjust = 0.2) +
    scale_y_continuous(name = "prop", labels = scales::percent)
  
  plt2 <- ggplot(plot.data %>% mutate(quarter = if_else(quarter > 4, "OT", as.character(quarter))), aes(quarter, fill = treatment, color = treatment)) +
    geom_bar(aes(y = stat(count/sum(count))), position = "identity", alpha = 0.2) +
    scale_y_continuous(name = "prop", labels = scales::percent)
  
  cmb <- plot_grid(plt1 + theme(plot.margin = unit(c(6,0,6,0), "pt"),
                                legend.position = "none"),
                   plt2 + theme(axis.title.y = element_blank(), 
                                plot.margin = unit(c(6,0,6,0), "pt"),
                                legend.position = "none"),
                   align = 'h') %>%
    plot_grid(., get_legend(plt1 + theme(legend.position = "bottom", 
                                         legend.justification = "center")), 
              ncol = 1, rel_heights = c(1,.2))
  
  return(cmb)
}

AddTitle <- function(p, t) {
  title <- ggdraw() + draw_label(t)
  plot_grid(title, p, ncol = 1, rel_heights = c(0.1, 1))
}

plot(PlotAux(mat.nobal) %>% AddTitle("No Balance"))

plot(PlotAux(mat.maha) %>% AddTitle("Maha"))

plot(PlotAux(mat.propensity.nocalip) %>% AddTitle("Propensity"))

plot(PlotAux(mat.propensity) %>% AddTitle("Propensity With Caliper"))

```

# Plotting covariate distributions

```{r, results = "hold"}

pallet_color <- scale_color_viridis_d("Treatment Group",
                                      labels = c("Control", "Timeouts"),
                                      option = "D",
                                      end = 0.5,
                                      aesthetics = c("colour", "fill"))

PlotLines <- function(data) {
  plt.lines <- dlply(data, .(method), function(dtf) {
    dtf %<>%
      mutate(treatment = factor(treatment))
    
    plt1 <- dtf %>%
      ggplot(aes(seconds, fill = treatment, color = treatment)) +
      geom_histogram(aes(y = stat(count / sum(count))), 
                     binwidth = 10, position = "identity", alpha = 0.15, size = 0.6) +
      scale_y_continuous(name = "prop", labels = function(x) paste0(x*100,"%")) +
      scale_x_continuous(name = expression(paste("seconds ", group("(",italic(S[t]),")")))) +
      pallet_color
    
    plt2 <- dtf %>% 
      mutate(quarter = if_else(quarter > 4, "OT", as.character(quarter))) %>%
      ggplot(aes(quarter, fill = treatment, color = treatment)) +
      geom_bar(aes(y = stat(count/sum(count))), 
               position = "identity", alpha = 0.15, size = 0.6) +
      scale_y_continuous(name = "prop", labels = function(x) paste0(x*100,"%")) +
      scale_x_discrete(name = expression(paste("quarter ", group("(",italic(Q[t]),")")))) +
      pallet_color
    
    plt3 <- dtf %>%
      ggplot(aes(margin, fill = treatment, color = treatment)) +
      geom_histogram(aes(y = stat(count / sum(count))),
                     binwidth = 2, position = "identity", alpha = 0.15, size = 0.6) +
      scale_y_continuous(name = "prop", labels = function(x) paste0(x*100,"%")) +
      scale_x_continuous(name = expression(paste("scoring margin ", group("(",italic(P[t]),")"))),
                         breaks = c(-30, 0, 30)) +
      pallet_color
    
    pltlist <- lst(plt1, plt2, plt3) %>%
      modify(~ .x + theme(legend.position = "none",
                          axis.title.y = element_blank(),
                          plot.margin = unit(c(6,0,6,0), "pt")))
    
    if(dtf$method[[1]] != "propensity.nocalip") {
      pltlist %<>%
        modify(~ .x + theme(axis.title.x = element_blank()))
    }
    
    cmb <- plot_grid(plotlist = pltlist,
                     align = 'h',
                     nrow = 1,
                     rel_widths = c(1.8,1,1))
    
    #method.name <- df$method[[1]]
    plt1 <- dtf %>%
      ggplot(aes(seconds, fill = treatment, color = treatment)) +
      geom_histogram(aes(y = stat(count / sum(count))), 
                     binwidth = 10, position = "identity", alpha = 0.15, size = 1) +
      pallet_color +
      theme_cowplot(font_size = 16) +
      theme(legend.title.align = 0)
    return(lst(cmb, plt1))
  })
}

AddLegend <- function(plts, labels = c("No-balance", "Mahalanobis", "Propensity")) {
  plotlist <- map(plts, "cmb")
    
  plt <- plot_grid(plotlist = plotlist, 
                   ncol = 1,
                   labels = labels,
                   label_x = 0.1,
                   hjust = 0.4,
                   label_size = 11) %>%
    plot_grid(get_legend(plts[[1]]$plt1 + theme(legend.position = "bottom",
                                                legend.justification = "center")),
              ncol = 1, 
              rel_heights = c(1,.08))
  return(plt)
}

plot.data <- all.mat %>%
  filter(method != "propensity")

# plot.data %>%
#   filter(match.poss == "home", delta == 2) %>%
#   PlotLines() %>%
#   AddLegend()
# SaveGraph("balance-delta2-all.pdf", height = 5)

plot.data %>%
  filter(match.poss == "home", delta == 4) %>%
  PlotLines() %>%
  AddLegend()
SaveGraph("balance-delta4-all.pdf", height = 6)

# plot.data %>%
#   filter(match.poss == "home", delta == 6) %>%
#   PlotLines() %>%
#   AddLegend()
# SaveGraph("balance-delta6-all.pdf", height = 5)

```

# Timeout effect distributions and causal effect

```{r, results = "hold"}

theplot1 <- function(df) {
  ggplot(df, aes(infl.score, color = treatment, fill = treatment)) +
    geom_density(data = filter(df, delta == 2), adjust = 2.5,  position = "identity", alpha = 0.15, size = 0.6) +
    geom_density(data = filter(df, delta == 4), adjust = 1.6,  position = "identity", alpha = 0.15, size = 0.6) +
    geom_density(data = filter(df, delta == 6), adjust = 1,  position = "identity", alpha = 0.15, size = 0.6) +
    facet_grid(~ delta, scales = "free") + 
    scale_y_continuous(name = "Density",
                       #labels = function(x) paste0(x*100,"%"),
                       breaks = pretty_breaks(4)) +
    scale_color_viridis_d("Treatment Group",
                          labels = c("Control", "Timeouts"),
                          end = 0.5, aesthetics = c("colour", "fill")) +
    scale_x_continuous(name = expr(Potential~Outcome~group("(",paste(Y^lambda,group("(",A[t]==a,")")),")")),
                       breaks = pretty_breaks(4))
}

# plot.data %>%
#   mutate(infl.score = if_else(match.poss == "away", -infl.score, infl.score)) %>%
#   ggplot(aes(infl.score, color = treatment, fill = treatment)) +
#   geom_density(data = filter(plot.data, delta == 2), adjust = 2.5,  position = "identity", alpha = 0.15, size = 0.6) +
#   geom_density(data = filter(plot.data, delta == 4), adjust = 1.6,  position = "identity", alpha = 0.15, size = 0.6) +
#   geom_density(data = filter(plot.data, delta == 6), adjust = 1,  position = "identity", alpha = 0.15, size = 0.6) +
#   facet_wrap(~ delta, scales = "fixed") + 
#   scale_y_continuous(name = "Density",
#                      #labels = function(x) paste0(x*100,"%"),
#                      breaks = pretty_breaks(4)) +
#   scale_color_viridis_d("Treatment Group",
#                         labels = c("Control", "Timeouts"),
#                         end = 0.5, aesthetics = c("colour", "fill")) +
#   scale_x_continuous(name = expr(Potential~Outcome~group("(",paste(Y^lambda,group("(",A[t]==a,")")),")")),
#                      breaks = pretty_breaks(4)) +
#   annotate("text", x = Inf, y = Inf, label = paste0("lambda==", config$deltas), hjust = 1, vjust = 1.5, parse = T)

theplot2 <- function(df) {
  ggplot(df, aes(infl.score, color = treatment, fill = treatment)) +
    geom_histogram(aes(y = stat(count / sum(count))),
                   data = filter(df, delta == 2), binwidth = 0.5,  position = "identity", alpha = 0.15, size = 0.6) +
    geom_histogram(aes(y = stat(count / sum(count))),
                   data = filter(df, delta == 4), binwidth = 0.3,  position = "identity", alpha = 0.15, size = 0.6) +
    geom_histogram(aes(y = stat(count / sum(count))),
                   data = filter(df, delta == 6), binwidth = 0.1,  position = "identity", alpha = 0.15, size = 0.6) +
    facet_grid(~ delta, scales = "free") + 
    scale_y_continuous(name = "Prop", labels = function(x) paste0(x*100,"%")) +
    scale_color_viridis_d("Treatment Group",
                          labels = c("Control", "Timeouts"),
                          end = 0.5, aesthetics = c("colour", "fill"))
}

theplot3 <- function(df, labels = c("No-balance", "Mahalanobis", "Propensity")) {
  pltlines <- df %>%
    dlply(.(method), function(dtf) { 
      dtf %>%
        theplot1() +
        annotate("text", x=Inf, y=Inf, 
                 label = paste0("lambda==",config$deltas), 
                 hjust = 1.6, vjust = 1.9, parse = T,
                 size = 4.5) +
        facet_wrap(delta ~ ., scales = "fixed") +
                   #labeller = label_bquote(cols = lambda==.(delta))) +
        theme(plot.margin = unit(c(6,0,0,0), "pt"),
              axis.title.y = element_blank(),
              strip.background = element_blank(),
              #strip.text = element_text(hjust = 0.8, size = rel(1)),
              strip.text = element_blank())
    })
  
  plt1 <- pltlines[[1]] + 
    geom_density(alpha = 0.15, size = 1) +
    theme_cowplot(font_size = 16) +
      theme(legend.title.align = 0)
  
  pltlines %<>%
    modify(~ .x %+% theme(plot.margin = unit(c(6,0,0,0), "pt"),
                          legend.position = "none",
                          axis.title.x = element_blank()))
  
  cmb <- plot_grid(plotlist = pltlines,
            ncol = 1,
            #align = "v",
            labels = labels,
            label_x = 0.05,
            label_y = 0.81,
            hjust = 0,
            vjust = 0,
            #hjust = -0.9,
            #vjust = 2.3,
            label_size = 11)
  
  plot_grid(cmb,
            NULL,
            get_legend(plt1 + theme(legend.position = "bottom",
                                    legend.justification = "center")),
            ncol = 1, 
            rel_heights = c(1,.04,.08))
}

plot.data <- all.mat %>%
  filter(method != "propensity")

# plot.data %>%
#     mutate(infl.score = if_else(match.poss == "away", -infl.score, infl.score)) %>%
#     theplot1() +
#     facet_wrap(method ~ delta, scales = "fixed", 
#                labeller = label_bquote(cols = lambda == .(delta)))

plot.data %>%
    mutate(infl.score = if_else(match.poss == "away", -infl.score, infl.score)) %>%
    theplot3()

SaveGraph("results-all.pdf", height = 5.5)


```

```{r}


```


```{r}


all.diff <- ldply(config$deltas, .fun = function(d) {
    all.diff.delta <- all.mat %>%
      filter(delta == d) %>%
      mutate(infl.score = if_else(match.poss == "away", -infl.score, infl.score)) %>%
      dlply(.(method, delta, match.poss), RunInferPermutation, .progress = "text")  %>% 
      RIPListToDataFrame()
    inform(paste0("Done delta = ", d))
    return(all.diff.delta)
  }) %>%
  as_tibble()

SaveObject(all.diff, folder = path("reports", "data"), name = "all.permutations.10m")

results.table <- all.diff %>%
  GetPValues(get.ci = F, filter.home = F, separate.effects = T)

results.table
  
deltas <- config$deltas
BrewTableResults <- function(tab.results, suffix.name, themethods = methods) {
  tab.results %<>% mutate_if(is.numeric, round, digits = 3)
  themethods
  
  brew.tab.results <- "\\begin{tabular}{lccccc} \\toprule
  Matching & $\\lambda$ & away.obs & away.p-value & home.obs & home.p-value \\\\ \\midrule
  <% for(m in themethods) { -%>
  <%= m %>
  <% for(d in deltas) { -%>
  <% data <- filter(tab.results, method == m, delta == d) -%>
  <% away.pv <- pull(data, away.p_value) -%> 
  <% home.pv <- pull(data, home.p_value) -%>
  & <%= d %> & <%= format(pull(data, away.obs.diff),nsmall=3) %> & <% if(!is.na(away.pv) && away.pv >= 0.01) { -%> 
  <%= format(away.pv,nsmall=3) -%> 
  <% } else { -%> \\signpvalue{<%= format(away.pv,nsmall=3) %>} <% } -%> 
  & <%= format(pull(data, home.obs.diff),nsmall=3) %> & <% if(!is.na(home.pv) && home.pv >= 0.01) { -%> 
  <%= format(home.pv,nsmall=3) -%> 
  <% } else { -%> \\signpvalue{<%= format(home.pv,nsmall=3) %>} <% } %> \\\\

  <% } %>
  <% } -%>
  \\bottomrule
  \\end{tabular}%"
  
  brew(text = brew.tab.results, output = path("reports", str_c("latex.table", suffix.name, "txt", sep = ".")))
}

BrewTableResults(results.table, str_c("results", year, sep = "."))

# all.mat %>%
#   mutate(infl.score = if_else(match.poss == "away", -infl.score, infl.score)) %>%
#   dlply(.(method, delta), RunInferPermutation, .parallel = T)  %>% 
#   RIPListToDataFrame() %>%
#   GetPValues(get.ci = F, filter.home = F)

```

# Other Results
## Last 5 minutes
```{r}
last5min.methods <- c(str_c(c("nobal", "maha",  "propensity.nocalip"), ".last5min"))
JoinAllMatchesAndDeltaWithData(methods = last5min.methods,
                               data = res.timeout.effect.data)
last5min.data <- env_get_list(global_env(), nms = str_c("mat", last5min.methods, sep = ".")) %>%
  modify(~ drop_na(., match.id)) %>%
  set_names(last5min.methods) %>%
  bind_rows(.id = "method") %>%
  mutate(method = fct_relevel(method, !!!last5min.methods))

last5min.data %<>%
  filter(season %in% c(2015, 2016, 2017, 2018)) %>%
  mutate(infl.score = if_else(match.poss == "away", -infl.score, infl.score))

last5min.results.table <- last5min.data %>%
  dlply(.(method, delta, match.poss), RunInferPermutation,
        .parallel = T) %>%
  RIPListToDataFrame() %>%
  GetPValues(get.ci = F, filter.home = F, separate.effects = T)

last5min.results.table

BrewTableResults(last5min.results.table, "last5min.results", themethods = last5min.methods)
```

```{r}
library(knitr)
library(kableExtra)

# all.mat %>%
#   group_by(method, delta) %>%
#   summarise(n = n()/2) %>%
#   arrange(delta) %>%
#   kable() %>%
#   kable_styling() %>%
#   scroll_box(width = "800px", height = "900px") %>%
#   save_kable(file = "reports/methods.html", self_contained = T)

DT::datatable(all.mat %>%
  group_by(method, delta, match.poss) %>%
  summarise(n = n()/2) %>%
  arrange(delta)) %>%
  htmlwidgets::saveWidget(path(projroot, "reports/methods.html"), selfcontained = TRUE)

# last5min.data %>%
#   group_by(method, delta, season) %>%
#   summarise(n = n()/2) %>%
#   arrange(delta) %>%
#   kable() %>%
#   kable_styling() %>%
#   scroll_box(width = "800px", height = "900px") %>%
#   save_kable(file = "reports/last5min.html", self_contained = T)

DT::datatable(last5min.data %>%
  group_by(method, delta, match.poss) %>%
  summarise(n = n()/2) %>%
  arrange(delta)) %>%
  htmlwidgets::saveWidget(path(projroot, "reports/last5min.html"), selfcontained = TRUE)
```

```{r}

all.results.table <- last5min.results.table %>%
  mutate(method = fct_relabel(method, ~ str_remove(.x, fixed(".last5min")))) %>%
  { bind_rows(last5min = ., all = results.table, .id = "kind") } %>%
  nest(-kind, -method, -delta, .key = "res") %>%
  spread(kind, res) %>%
  unnest(.sep = ".")

BrewTableAllResults <- function(tab.results, suffix.name, themethods = methods) {
  tab.results %<>% mutate_if(is.numeric, round, digits = 3)
  deltas <- config$deltas
  tab.methods <- themethods %>%
    as_list() %>%
    set_names(themethods) %>%
    list_modify(unmatch = "Before Matching", nobal = "No-balance", 
                maha = "Mahalanobis", propensity.nocalip = "Propensity",
                propensity = "Propensity with caliper") %>%
    squash_chr() %>%
    extract(themethods) %>%
    rep(length(config$deltas))
  
  brew.tab.results <- "\\begin{tabular}{llcccc} \\toprule
  & & \\multicolumn{2}{c}{All Game} & \\multicolumn{2}{c}{Last 5 Minutes} \\\\
  \\cmidrule(lr){3-4}
  \\cmidrule(lr){5-6}
  $\\lambda$ & Method & \\TEaway & \\TEhome & \\TEaway & \\TEhome \\\\ \\midrule
  <% for(d in deltas) { -%>
  <%= d -%>
  <% for(m_i in 1:length(themethods)) { -%>
  <% data <- filter(tab.results, method == themethods[[m_i]], delta == d) -%>
  <% all.away.pv <- pull(data, all.away.p_value) -%>
  <% all.home.pv <- pull(data, all.home.p_value) -%>
  <% last.away.pv <- pull(data, last5min.away.p_value) -%>
  <% last.home.pv <- pull(data, last5min.home.p_value) -%>
& <%= tab.methods[[m_i]] %> & <%= format(pull(data, all.away.obs.diff),nsmall=3) -%>
<% if(!is.na(all.away.pv) && all.away.pv < 0.01) { -%>\\signobs <% } -%> 
& <%= format(pull(data, all.home.obs.diff),nsmall=3) -%>
<% if(!is.na(all.home.pv) && all.home.pv < 0.01) { -%>\\signobs <% } -%>
& <%= format(pull(data, last5min.away.obs.diff),nsmall=3) -%>
<% if(!is.na(last.away.pv) && last.away.pv < 0.01) { -%>\\signobs <% } -%> 
& <%= format(pull(data, last5min.home.obs.diff),nsmall=3) -%>
<% if(!is.na(last.home.pv) && last.home.pv < 0.01) { -%>\\signobs <% } %> 
  \\\\ 
  <% } -%>
  <% } -%> 
  \\bottomrule
  \\end{tabular}%"
  
  #if (SAVE_OUTPUT) brew(text = brew.tab.results, output = path("reports", str_c("latex.table", suffix.name, "txt", sep = ".")))
  brew(text = brew.tab.results, output = path("reports", str_c("latex.table", suffix.name, "txt", sep = ".")))
}

BrewTableAllResults(all.results.table, str_c("all.results", year, sep = "."))
```


## By team
```{r, results = "hold"}

aux.data <- all.mat %>%
  filter(method == "propensity.nocalip") %>%
  mutate(method = fct_drop(method)) %>%
  mutate(infl.score = if_else(match.poss == "away", -infl.score, infl.score)) %>%
  filter(delta == 4)

tab.results <- aux.data %>%
  dlply(.(method, delta, match.poss, team), RunInferPermutation, 
        .parallel = TRUE) %>%
  RIPListToDataFrame() %>%
  GetPValues(get.ci = F, filter.home = F, separate.effects = T)

tab.results

```

```{r, include = FALSE}
# map_dfr(config$deltas %>% set_names(config$deltas), function(d) {
#   map_dfc(list(nobal = mat.nobal, 
#                maha = mat.maha, 
#                mahar = mat.maha.replace, 
#                prop = mat.propensity), 
#           function(df) {
#             df %>%
#               filter(delta == d, match.poss == "home") %>%
#               drop_na(match.id) %>%
#               summarise(eff.treat = weighted.mean(infl.score, A == 1),
#                         eff.contr = weighted.mean(infl.score, A == 0),
#                         eff = eff.treat - eff.contr) %>%
#               pull(eff) %>%
#               round(4)
#           })
# }, .id = "delta")

# map_dfr(set_names(config$deltas, config$deltas), function(d) {
#   all.mat %>%
#     filter(delta == d, match.poss == "home") %>%
#     group_by(method) %>%
#     summarise(eff.treat = weighted.mean(infl.score, A == 1),
#               eff.contr = weighted.mean(infl.score, A == 0),
#               eff = round(eff.treat - eff.contr, 4)) %>%
#     select(method, eff) %>%
#     spread(method, eff)
# }, .id = "delta")

```

```{r, results = "hold"}
# plot.data <- bind_rows(unmatch = mat.propensity %>% filter(A == 1),
#                        matched = mat.propensity %>% filter(A == 1, !is.na(match.id)),
#                        .id = "situation")
# 
# ggplot(plot.data, aes(slope.before, fill = situation)) +
#   facet_grid(delta~.) +
#   geom_density(position = "identity", alpha = 0.50, adjust = 1.2)
# #ggsave(path(projroot, "graphs", "unmatch-match.pdf"), device = "pdf", width = 7.28, height = 4)

```

```{r, include = FALSE, results = "hold"}
# plotCovars <- function(plot.data) {
#   plt1 <- ggplot(plot.data, aes(slope.before)) +
#     facet_grid(treatment~delta) +
#     labs(title = "slope.before") +
#     geom_bar()
#   plt2 <-  ggplot(plot.data, aes(seconds)) +
#     facet_grid(treatment~delta) +
#     labs(title = "seconds") +
#     geom_histogram(binwidth = 30)
#   plt3 <- ggplot(plot.data, aes(quarter)) +
#     facet_grid(treatment~delta) +
#     labs(title = "quarter") +
#     geom_bar()
#   plt4 <- ggplot(plot.data, aes(margin)) +
#     facet_grid(treatment~delta) +
#     labs(title = "margin") +
#     geom_bar()
#   list(plt1, plt2, plt3, plt4)
# }
# plot.data <- bind_rows(maha = mat.maha, propensity = mat.propensity, .id = "method") %>%
#   drop_na(match.id)
# 
# newPlots <- function(pltdata, var, use_bar = FALSE, bins = 20) {
#   plt <- ggplot(pltdata, aes_string(x = var, fill = "treatment")) +
#     facet_grid(method~delta, scales = "free_y")
#   if (use_bar) {
#     plt <- plt + geom_bar(position = "identity", alpha = 0.5)
#   } else {
#     plt <- plt + geom_histogram(position = "identity", alpha = 0.50, bins = bins) 
#   }
#   return(plt)
# }
# 
# newPlots(plot.data, "seconds")
# ggsave(path(projroot, "graphs", "covar-seconds-balance.pdf"), device = "pdf", width = 7.28, height = 4)
# 
# newPlots(plot.data, "quarter", use_bar = T)
# ggsave(path(projroot, "graphs", "covar-quarter-balance.pdf"), device = "pdf", width = 7.28, height = 4)

# plts <- plotCovars(plot.data %>% filter(method == "maha"))
# plts[[1]]
# plts[[2]]
# plts[[3]]
# plts[[4]]
```


```{r, include = FALSE}
# mat.nobal %>%
#   drop_na(match.id) %>%
#   group_by(delta, team, poss, A) %>%
#   summarise_at(vars(infl.score), mean) %>%
#   group_by(delta, team, poss) %>%
#   mutate(effect = infl.score - lag(infl.score)) %>%
#   summarise(effect = last(effect)) %>% ungroup() %>%
#   mutate(effect = if_else(poss == "away", -effect, effect)) %>%
#   arrange(delta, poss, desc(effect)) %T>% print(n=2000) %>%
#   spread(delta, effect, sep= ".")
# ```
# ```{r}
# PerformPermTest <- function(mat.data) {
#   mat.data %>%
#     group_by(delta, team, poss) %>%
#     do(perm.test = oneway_test(infl.score ~ as.factor(A), ., distribution = approximate(B = 10000)))
# }
# 
# PerformPermTest(mat.nobal %>% drop_na(match.id))
```
